Cognate beginnings to bilingual lexical acquisition

### 2023-07-25 docs/index.qmd
Update Dockerfile

---
---

@@

![arXiv](https://info.arxiv.org/brand/images/brand-logo-primary.jpg){height=100px}

![OSF](https://www.datacc.org/wp-content/uploads/2020/03/osf.png){height=100px}

![GitHub](https://upload.wikimedia.org/wikipedia/commons/thumb/9/91/Octicons-mark-github.svg/2048px-Octicons-mark-github.svg.png){height=100px}

@@

>>>>

@@

![arXiv](https://info.arxiv.org/brand/images/brand-logo-primary.jpg){height="100px"}

![OSF](https://www.datacc.org/wp-content/uploads/2020/03/osf.png){height="100px"}

![GitHub](https://upload.wikimedia.org/wikipedia/commons/thumb/9/91/Octicons-mark-github.svg/2048px-Octicons-mark-github.svg.png){height="100px"}

@@

# Data dictionaries

```{r}
#' Create data dictionary for a dataframe and save as CSV in the docs/ folder
#' 
#' @param x Data frame for which to create a data dictionary
data_dict <- function(x) {
    if (!(is.data.frame(x) | tibble::is_tibble(x))) {
        cli::cli_abort("x must be a dataframe or tibble")
    }

    nmissing <- function(x) sum(is.na(x))
    nlevels <- function(x) length(unique(x))

    # describe character variables
    x_character <- x |> 
        summarise(across(where(\(x) is.character(x) | is.factor(x)),
                         tibble::lst(nmissing, nlevels),
                         .names = "{.col}.{.fn}"))

    # describe numeric variables
    numeric.fns <- tibble::lst(nmissing, mean, median, sd, min, max)
    x_numeric <- x |> 
        summarise(across(where(is.numeric), 
                         numeric.fns,
                         .names = "{.col}.{.fn}"))

    # join
    out <- bind_cols(x_character, x_numeric) |> 
        pivot_longer(everything(),
                     names_to = c("variable", "measure"),
                     values_to = "value",
                     names_sep = "\\.", ) |> 
        pivot_wider(id_cols = variable,
                    names_from = "measure",
                    values_from = "value",
                    values_fn = \(x) ifelse(is.character(x),
                                            paste0(x, collapse = ","),
                                            unlist(x)))

    return(out)
}
```

::: {.callout-info}

## Items

:::

### 2023-07-25 manuscript/manuscript.qmd
Update Dockerfile

In adult bilingual populations, language dominance and proficiency are frequently defined using dimensions other than degree of exposure, which is a more common practice in infant research [@marian2021measuring; @rocha2023defining]. For instance, low-proficiency bilinguals in many of the aforementioned studies acquired their second language years after their toddlerhood. We identify three critical ways in which this prevents a clear comparison between our results and those from studies on second language acuquisition in adults. First, in adult second language acquisition, the acquisition of the phonology of the new language must be negotiated with the already acquired phoneme inventory of the first language [e.g., @cutler2006asymmetric; @sebastian2006first], in place around the first year of life [see @werker2015critical for review]. Second, adults acquiring a second language already possess a system of form-meaning mappings, whereas simulatenous bilingual infants must build a lexicon for two languages in the absence of clear form-meaning mappings. Third, adults are assumed to be literate and to possess an orthographic system in place, which may shape how new words are integrated in the lexicon and processed during experimental tasks [e.g., @thierry2007brain]. In this scenario, the acquisition of a second language may take place in a substantially different way compared to how bilingual infants acquire two languages from birth. A more similar case to the one concerning the present study is considered by the DevLex-II model [@zhao2010bilingual], which captures unique features of the early bilingual lexicon, and considers the case of infants stimultaneously acquiring their two language. In line with the adult models, DevLex-II predicts asymmetries between word representation from the dominant and the non-dominant language. Simulations from DevLex-II result in an asymmetric cross-language priming, in which words from the dominant (acquired acquired) language primed more strongly the recognition of words in the non-dominant language (later acquired) than in the other direction [@zhao2013simulating].

In summary, there is a compelling case for attributing aymmetric effects of parallel activation to differences in activation strength between forward and backward connections. It is nonethless possible that, as argued in the introduction, the asymmetric effect of cognateness found in the present study is simply the result of infants being exposed more frequently to words in the dominant language than to words in the non-dominant language. This would lead to words in the non-dominant language receiving additional parallel activation, compared to words in the dominant language, and therefore benefitting more strongly from their cognate status. These two accounts are not mutually exclusive, as words in the dominant language may active more *strongly* their translations than *vice versa*, on top of such activation being more frequent. Further research is needed in order to clarify this issue.

>>>>

In adult bilingual populations, language dominance and proficiency are frequently defined using dimensions other than degree of exposure, which is a more common practice in infant research [@marian2021measuring; @rocha2023defining]. For instance, low-proficiency bilinguals in many of the aforementioned studies acquired their second language years after their toddlerhood. We identify three critical ways in which this prevents a clear comparison between our results and those from studies on second language acquisition in adults. First, in adult second language acquisition, the acquisition of the phonology of the new language must be negotiated with the already acquired phoneme inventory of the first language [e.g., @cutler2006asymmetric; @sebastian2006first], in place around the first year of life [see @werker2015critical for review]. Second, adults acquiring a second language already possess a system of form-meaning mappings, whereas simultaneous bilingual infants must build a lexicon for two languages in the absence of clear form-meaning mappings. Third, adults are assumed to be literate and to possess an orthographic system in place, which may shape how new words are integrated in the lexicon and processed during experimental tasks [e.g., @thierry2007brain]. In this scenario, the acquisition of a second language may take place in a substantially different way compared to how bilingual infants acquire two languages from birth. A more similar case to the one concerning the present study is considered by the DevLex-II model [@zhao2010bilingual], which captures unique features of the early bilingual lexicon, and considers the case of infants simultaneously acquiring their two language. In line with the adult models, DevLex-II predicts asymmetries between word representation from the dominant and the non-dominant language. Simulations from DevLex-II result in an asymmetric cross-language priming, in which words from the dominant (acquired acquired) language primed more strongly the recognition of words in the non-dominant language (later acquired) than in the other direction [@zhao2013simulating].

In summary, there is a compelling case for attributing asymmetric effects of parallel activation to differences in activation strength between forward and backward connections. It is nonetheless possible that, as argued in the introduction, the asymmetric effect of cognateness found in the present study is simply the result of infants being exposed more frequently to words in the dominant language than to words in the non-dominant language. This would lead to words in the non-dominant language receiving additional parallel activation, compared to words in the dominant language, and therefore benefiting more strongly from their cognate status. These two accounts are not mutually exclusive, as words in the dominant language may active more *strongly* their translations than *vice versa*, on top of such activation being more frequent. Further research is needed in order to clarify this issue.
